`{peacesciencer}`: An R Package for Quantitative Peace Science Research

### 2022-01-14 manuscript/ms.Rmd
fira code

---
title: "`{peacesciencer}`: An R Package for Quantitative Peace Science Research"
thanks: "Replication files are available on the author's Github account (https://github.com/svmiller/peacesciencer). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
author:
- name: Steven V. Miller
  affiliation: Clemson University
bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
# bibliography: inst/refs.bib
abstract: "This article introduces `{peacesciencer}`, an R package that contains a litany of tools for creating data of widespread interest to the peace science community. The package is cross-platform, assuming only a somewhat recent installation of the R programming language with some of the enhanced functionality of the broadly popular `{tidvyerse}` packages. Peace science researchers can use this package to greatly reduce the time needed to perfectly recreate common types of data from scratch and to merge in ubiquitous indicators included in almost every analysis (e.g. democracy data, contiguity data). The software is freely available on CRAN and maintains an active website documenting its features at `r params$ps_website`."
keywords: "software, statistical analysis, peace science, reproducibility"
geometry: margin=1in
csl: inst/jpr.csl
mainfont: cochineal
#sansfont: Linux Biolinum O 
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
  ps_website: ""
  ps_manuals: ""
  ps_github: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
nocite: |
  @cartersmith2020fml, @marshalletal2017p, @coppedgeetal2020vdem, @gleditschetal2002ac, @thompsondreyer2012hir, @cowstates2016, @stinnettetal2002cow, @pevehouseetal2020tow, @schvitz2021mis, @palmeretal2021mid5, @singer1987rcwd, @nardulli2012creg, @gledtischward1999rlis, @nunnpuga2012r, @haege2011cc, @pettersson2019ov, @leedsetal2002atop, @barbierietal2009td
#always_allow_html: TRUE
header-includes:
  - \usepackage{longtable}
  - \usepackage{booktabs}
  - \usepackage{csquotes}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
#  - \let\BeginKnitrBlock\begin \let\EndKnitrBlock\end
#  - \usepackage{colortbl}
#  - \arrayrulecolor{black}
#  - \usepackage{threeparttable}
#  - \usepackage{threeparttablex}
#  - \midrule\relax
---

>>>>

---
title: "`{peacesciencer}`: An R Package for Quantitative Peace Science Research"
thanks: "Replication files are available on the author's Github account (https://github.com/svmiller/peacesciencer). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com."
author:
- name: Steven V. Miller
  affiliation: Clemson University
bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
# bibliography: inst/refs.bib
abstract: "This article introduces `{peacesciencer}`, an R package that contains a litany of tools for creating data of widespread interest to the peace science community. The package is cross-platform, assuming only a somewhat recent installation of the R programming language with some of the enhanced functionality of the broadly popular `{tidvyerse}` packages. Peace science researchers can use this package to greatly reduce the time needed to perfectly recreate common types of data from scratch and to merge in ubiquitous indicators included in almost every analysis (e.g. democracy data, contiguity data). The software is freely available on CRAN and maintains an active website documenting its features at `r params$ps_website`."
keywords: "software, statistical analysis, peace science, reproducibility"
geometry: margin=1in
csl: inst/jpr.csl
mainfont: cochineal
monofont: Fira Code
#sansfont: Linux Biolinum O 
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
  removetitleabstract: ""
  ps_website: ""
  ps_manuals: ""
  ps_github: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
removetitleabstract: "`r params$removetitleabstract`"
nocite: |
  @cartersmith2020fml, @marshalletal2017p, @coppedgeetal2020vdem, @gleditschetal2002ac, @thompsondreyer2012hir, @cowstates2016, @stinnettetal2002cow, @pevehouseetal2020tow, @schvitz2021mis, @palmeretal2021mid5, @singer1987rcwd, @nardulli2012creg, @gledtischward1999rlis, @nunnpuga2012r, @haege2011cc, @pettersson2019ov, @leedsetal2002atop, @barbierietal2009td
#always_allow_html: TRUE
header-includes:
  - \usepackage{longtable}
  - \usepackage{booktabs}
  - \usepackage{csquotes}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
  - \usepackage{setspace}
#  - \let\BeginKnitrBlock\begin \let\EndKnitrBlock\end
#  - \usepackage{colortbl}
#  - \arrayrulecolor{black}
#  - \usepackage{threeparttable}
#  - \usepackage{threeparttablex}
#  - \midrule\relax
---
